\documentclass[11pt,oneside,a4paper]{article}
\usepackage[left=0.50in,top=0in,right=0.50in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\begin{document}
	\title{\bf Ameena Sana}
	
	\author{ {\bf Email:} {ameena@quintype.com;} \thinspace {\bf phone:}{8147467455;}}
	\date{}
	
	
	
	\maketitle
	
	\section*{Educational Qualification}
	\begin{itemize}
		
		\item {\bf B.E(ECE)},Prodhadevaraya institute of technology Hospet, 
		 ,Karnataka,2018
		
		\item 
		{\bf P.U.C(PCMB)},S.G college,Koppal,Karnataka,2014
		
		\item  {\bf SSLC},Trinity public school,Koppal,Karnataka,2012
		
	\end{itemize}
	
	
	\section*{Personal Details}
	
	\begin{itemize}
		\item Date of Birth:28-02-1997.
		\item Language known: English,Hindi,Kannada.
		\item Address:Ganesh Nagar,Koppal.
		
	\end{itemize}
	
	\section*{Technical skills}
	\begin{itemize}
		
	\item Programming Languages: C , Java.
	\item Web Technologies: HTML,CSS,JS.
	
	\end{itemize}

\section{Academic Project}
\begin{itemize}
	
	\item TITLE : Raspberry Pi based assistive communication for deaf,dumb and blind people.
	\item DESCRIPTION : Prototype model for model for blind,deaf and dumb people by employing a single compact device.The visually impaired people can able to understand the words easily.
	\item TEAM SIZE: 3.
	\end{itemize}
	
\section{Extra curricular activities}
\begin{itemize}
\item Participated in events conducted by the college like Technical quiz,tech charades etc..
\item Voluntered for many events in the college such as blood donation camp. 
\end{itemize}	

	

\end{document}		



